---
title: tableschema
output: 
  github_document:
    html_preview: no
  number_sections: yes
---

[![Build Status](https://travis-ci.org/okgreece/tableschema-r.svg?branch=master)](https://travis-ci.org/okgreece/tableschema-r)
[![Coverage Status](https://coveralls.io/repos/github/okgreece/tableschema-r/badge.svg?branch=master)](https://coveralls.io/github/okgreece/tableschema-r?branch=master)
[![Github Issues](http://githubbadges.herokuapp.com/okgreece/tableschema-r/issues.svg)](https://github.com/okgreece/tableschema-r/issues)
[![Pending Pull-Requests](http://githubbadges.herokuapp.com/okgreece/tableschema-r/pulls.svg)](https://github.com/okgreece/tableschema-r/pulls)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![packageversion](https://img.shields.io/badge/Package%20version-0.0.0.9000-orange.svg?style=flat-square)](commits/master)
[![minimal R version](https://img.shields.io/badge/R%3E%3D-3.1-6666ff.svg)](https://cran.r-project.org/)
[![Licence](https://img.shields.io/badge/licence-MIT-blue.svg)](https://opensource.org/licenses/MIT)
[![Gitter](https://img.shields.io/gitter/room/nwjs/nw.js.svg)](https://gitter.im/frictionlessdata/chat)
```{r, eval=FALSE, include=FALSE}
# [![Project Status: Inactive – The project has reached a stable, usable state but is no longer being actively developed; support/maintenance will be provided as time allows.](http://www.repostatus.org/badges/latest/inactive.svg)](http://www.repostatus.org/#inactive)

```



R library for working with [Table Schema][tableschema].

# Features

+ `Table` class for working with data and schema
+ `Schema` class for working with schemas
+ `Field` class for working with schema fields
+ `validate` function for validating schema descriptors
+ `infer` function that creates a schema based on a data sample

# Getting started

## Installation

```{r, eval=FALSE, include=T}
install.packages("devtools")
```


```{r, eval=FALSE, include=T}
devtools::install_github("okgreece/tableschema-r")
```

# Documentation

## Table

A table is a core concept in a tabular data world. It represents a data with a metadata (Table Schema). 
Let's see how we could use it in practice.

## Schema

## Field


Table below shows the available types, formats and resultant value of the cast:

+-----------+-----------------------------+------------------+
| Type      | Formats                     | Casting result   |
+:==========+:============================+:=================+
| any       | default                     | Any              |
+-----------+-----------------------------+------------------+
| array     | default                     | Array            |
+-----------+-----------------------------+------------------+
| boolean   | default                     | Boolean          |
+-----------+-----------------------------+------------------+
| date      | default, any                | Date             |
+-----------+-----------------------------+------------------+
| datetime  | default, any                | Date             |
+-----------+-----------------------------+------------------+
| duration  | default                     | Duration         |
+-----------+-----------------------------+------------------+
| geojson   | default, topojson           | Object           |
+-----------+-----------------------------+------------------+
| geopoint  | default, array, object      | [Number, Number] |
+-----------+-----------------------------+------------------+
| integer   | default                     | Number           |
+-----------+-----------------------------+------------------+
| number    | default                     | Number           |
+-----------+-----------------------------+------------------+
| object    | default                     | Object           |
+-----------+-----------------------------+------------------+
| string    | default, uri, email, binary | String           |
+-----------+-----------------------------+------------------+
| time      | default, any                | Date             |
+-----------+-----------------------------+------------------+
| year      | default                     | Number           |
+-----------+-----------------------------+------------------+
| yearmonth | default                     | [Number, Number] |
+-----------+-----------------------------+------------------+


## Changelog - News

In [NEWS.md][news] described only breaking and the most important changes. The full changelog could be found in nicely formatted [commit][commits] history.  

# Github

+ https://github.com/okgreece/tableschema-r

[tableschema]: http://specs.frictionlessdata.io/table-schema/
[news]: https://github.com/okgreece/tableschema-r/blob/master/NEWS.md
[commits]: https://github.com/okgreece/tableschema-r/commits/master